```{r}
library(prob)
library(tidyverse)
library(janitor)
library(assertr)
library(fastGraph)
library(infer)
library(e1071)
```

```{r}
library(ggplot2)
```

```{r}

data(msleep)
```

```{r}
msleep %>% 
  clean_names()
dim(msleep)
names(msleep)
head(msleep)
tail(msleep)
glimpse(msleep)

```

```{r}
mean(msleep$sleep_total)
```

H_0: mean_sleep_total(msleep) == mean_sleep_total(jabberwockies) = 7
H_a: mean_sleep_total(msleep) != mean_sleep_total(jabberwockies) = 7
```{r}
jabberwocky_sleep <- 7
sleep_stats <- msleep %>% 
  summarise(mean_sleep = mean(sleep_total)) 

sleep_stats %>% 
  summarise(diff_sleep = mean_sleep - jabberwocky_sleep)


```

```{r}
sample_sleep <- msleep %>% 
  rep_sample_n(size = 200, replace = TRUE, reps = 1)
sample_sleep
```

```{r}
threshold <- 0.05
ci_sleep <- 
```
H_0: mean_sleep(omni) is significantly longer than mean_sleep(carni)
H_a: mean_sleep(omni) is NOT significantly longer than mean_sleep(carni)
```{r}
Average_sleep_omni <- msleep %>% 
  filter(vore == "omni") %>% 
  summarise(mean_sleep = mean(sleep_total))

Average_sleep_carni <- msleep %>% 
  filter(vore == "carni") %>% 
  summarise(mean_sleep = mean(sleep_total))

Diff_in_sleep <- msleep %>% 
  summarise(Average_sleep_omni - Average_sleep_carni)
```
H_0: Proportion of domesticated animals in population is greater than 5%
H_a: Proportion of domesticated animals in population is not greater than 5%
```{r}
dom_animals <-  msleep %>% 
  mutate(is_domesticated = conservation == "domesticated")
dom_stats <- dom_animals %>% 
  specify(response = is_domesticated, success = )
```


```{r}
dom_distribution <- msleep %>% 
  filter(conservation == "domesticated") %>% 
  specify(response = conservation, success = "domesticated") %>%  
  hypothesise(null = "point", p = 0.05) %>% 
  generate(reps = 1000, type = "draw") %>% 
  calculate(stat = "prop")
```


```{r}
```

Q1.2
# 