```{r}
library(prob)
library(tidyverse)
library(CodeClanData)
library(janitor)
library(assertr)

```
# Q1.  The purpose of this investigation is to get a glimpse of the dataset about phones to see what I'm dealing with for the MVP.  I've called up the basic functions for skimming through a dataset, and I will probably have to get rid of data that has NAs in it for accuracy sake.  
```{r}
phone_data <- read_csv('data/20190928-items.csv') %>% 
  clean_names()
phone_data
head(phone_data)
tail(phone_data)
names(phone_data)
dim(phone_data)
sum(is.na(phone_data))
drop_na(phone_data)

```
Q2
# The purpose of this question is to find the brand with the most phones in the dataset. I found the best method to get an answer was to create a mode function, which I learned from stackoverflow.  It seems to function fine and all credit to them.    
```{r}
most_phones <- phone_data %>%
   
  summarise(which.max(brand))
most_phones
```

```{r}
get_mode <- function(x){
  return(names(sort(table(x), decreasing = T, na.last = T)[1]))
}

get_mode(phone_data$brand)
```

```{r}
phone_data2 <- phone_data %>% 
  # select(brand) %>% 
  group_by(brand) %>% 
  mutate(sales = count(brand))
```

Q3
# For this question, I must plot the distribution of the top ratings for Samsung, and see if the normal distribution gives an accurate idea of how the ratings are spread out.  
```{r}
```


```{r}
rating_stats <- phone_data %>% 
  filter(brand == "Samsung") %>% 
  summarise(num = n(),
            mean = mean(rating),
            sd = sd(rating))

rating_stats
```


```{r}
phone_data %>% 
  filter(brand == "Samsung") %>% 
  ggplot(aes(x = title)) +
  geom_histogram(aes(y = ..count..), col = "white",
                 bins = 50) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = rating_stats$mean,
      sd = rating_stats$sd
    ), 
    col = "red"
  )
```

```{r}

```

