```{r}
library(tidyverse)
library(CodeClanData)
library(janitor)
library(assertr)
library(readr)
library(ggplot2)
```

```{r}
library(ggplot2)

# Create Data
data <- data.frame(
  group=LETTERS[1:5],
  value=c(13,7,9,21,2)
)

# Basic piechart
ggplot(data, aes(x="", y=value, fill=group)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  
  theme_void()
```
The purpose of this code chunk to quickly inspect the backpack data and to familiarise oneself with it prior to solving the Analysis questions with it.
Q1
```{r}
backpack
dim(backpack)
names(backpack)
head(backpack)
tail(backpack)
glimpse(backpack)
sum(is.na(backpack))
```
The purpose of this point plot is to show the distribution of the weight that students are carrying per school year.  
Q2
```{r}
backpack %>% 
  ggplot(aes(x = year, y = backpack_weight, colour = major)) +
  geom_point()
```
Q3
```{r}
Backpack_weights <- backpack %>% 
  group_by(sex) %>% 
  summarise(mean_weight = mean(backpack_weight))

ggplot(Backpack_weights, aes(x = sex, y = mean_weight)) +
  geom_col()
```

Q4: Correlation between body weight and backpack weight
```{r}
backpack %>% 
  ggplot(aes(x = year, y = backpack_weight, fill = body_weight)) +
  geom_col() +
  labs(x = "Year", y = "Backpack weight")
```
Q5: Correlation of body weight and backpack weight between genders
```{r}
backpack_F <- backpack %>% 
  filter(sex == "Female")

backpack_M <- backpack %>% 
  filter(sex == "Male")
 
  ggplot(backpack_F, aes(x = year, y = backpack_weight, fill = body_weight)) +
  geom_col() +
  labs(x = "Year", y = "Backpack weight")
  
  ggplot(backpack_M, aes(x = year, y = backpack_weight, fill = body_weight)) +
  geom_col() +
  labs(x = "Year", y = "Backpack weight")
```
Q6: Pie chart for proportion
```{r}
backpack %>% 
  ggplot(aes(x = back_problems, y = major)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0)

```

