```{r}
library(tidyverse)
library(CodeClanData)
library(janitor)
library(assertr)
library(readr)
library(ggplot2)
```

```{r}
library(ggplot2)

# Create Data
data <- data.frame(
  group=LETTERS[1:5],
  value=c(13,7,9,21,2)
)

# Basic piechart
ggplot(data, aes(x="", y=value, fill=group)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  
  theme_void()
```
The purpose of this code chunk to quickly inspect the backpack data and to familiarise oneself with it prior to solving the Analysis questions with it.
Q1
```{r}
backpack
dim(backpack)
names(backpack)
head(backpack)
tail(backpack)
glimpse(backpack)
sum(is.na(backpack))
```
The purpose of this histogram is to show the distribution of the weight that students are carrying by showing the number of backpacks against the weight of the backpacks.  
Q2
```{r}
backpack %>% 
  ggplot(aes(x =backpack_weight)) +
  geom_histogram(bins = 20, col = "white", fill = "dark green") +
                   theme_light() +
                   labs(y = "number of backpacks", x = "weight")
                   
```
The purpose of this histogram is to show the backpack weight distribution by gender.
Q3
```{r}
# Backpack_weights <- backpack %>% 
#   group_by(sex) %>% 
#   summarise(mean_weight = mean(backpack_weight))

ggplot(backpack, aes(x = backpack_weight, fill = sex)) +
  scale_fill_manual(values = c("green", "blue")) +
  
  geom_histogram(bins = 20, col = "white", show.legend = FALSE) +
  theme_light() +
  labs(y = "number of backpacks", x = "weight") +
  facet_wrap(~ sex, nrow = 2) +
  coord_flip()

```

```{r}
ggplot(backpack) +
  aes(x = backpack_weight, fill = sex) +
  scale_fill_manual(values=c('#E69F00', '#56B4E9')) +
  geom_histogram(bins = 20, col = "white", show.legend = FALSE) + 
  theme_light() + 
  labs(y = "number of backpacks", x = "weight") + 
  facet_wrap(~ sex, nrow = 2)
```
The purpose of this graph is to show a relationship between the body weight of a person and the weight of their backpack.

Q4: Correlation between body weight and backpack weight
```{r}
backpack %>% 
  ggplot(aes(x = body_weight, y = backpack_weight)) +
  geom_point() +
  labs(x = "Body Weight", y = "Backpack weight")
```
Classnotes Q5
```{r}
ggplot(backpack) + 
  aes(x = body_weight, y = backpack_weight, color = sex) + 
  geom_point() + 
  facet_wrap(~sex) + 
    scale_color_manual(values=c('#E69F00', '#56B4E9'))+
    labs(x = "body weight", y = "backpack weight")
```

Q5: Correlation of body weight and backpack weight between genders
```{r}
backpack_F <- backpack %>% 
  filter(sex == "Female")

backpack_M <- backpack %>% 
  filter(sex == "Male")
 
  ggplot(backpack_F, aes(x = year, y = backpack_weight, fill = body_weight)) +
  geom_col() +
  labs(x = "Year", y = "Backpack weight")
  
  ggplot(backpack_M, aes(x = year, y = backpack_weight, fill = body_weight)) +
  geom_col() +
  labs(x = "Year", y = "Backpack weight")
```

```{r}
ggplot(backpack) + 
  aes(x = body_weight, y = backpack_weight, color = sex) + 
  geom_point() + 
  facet_wrap(~sex) + 
    scale_color_manual(values=c('#E69F00', '#56B4E9'))+
    labs(x = "body weight", y = "backpack weight")
```

Q6: Pie chart for proportion
```{r}
backpack %>% 
  ggplot(aes(x = back_problems, y = major)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0)

```

```{r}
backpack <- backpack %>%
  mutate(backpain_labelled = recode(back_problems, 
                       "0" = "No", 
                       "1" = "Yes"))

ggplot(backpack) + 
  aes(x = backpain_labelled, fill = backpain_labelled) + 
  geom_bar() +
ylim(0,100) + 
  labs(x = "backpain reported", y = "student count") +
    scale_fill_manual(values=c('#f0ca41', '#5022bd'))+
theme(legend.position = "none")
```
Q7
```{r}
ggplot(backpack) + 
  aes(x = backpain_labelled, fill = backpain_labelled) + 
  geom_bar() +
  labs(x = "backpain reported", y = "student count") + 
  facet_wrap(~sex) +
      scale_fill_manual(values=c('#f0ca41', '#5022bd'))+
theme(legend.position = "none")
```
Q8
```{r}
pain_labels <- c("backpain: no", "backpain: yes")
names(pain_labels) <- c("No", "Yes")

sex_labels <- c("sex: female", "sex: male")
names(sex_labels) <- c("Female", "Male")


ggplot(backpack) + 
  aes(x = body_weight, y = backpack_weight, color = backpain_labelled) + 
  geom_point() + 
  facet_grid(sex ~ backpain_labelled, 
             labeller = labeller(backpain_labelled = pain_labels, sex = sex_labels)) + 
  labs(x = "\n body weight", y = "backpack weight \n") +
      scale_color_manual(values=c('#f0ca41', '#5022bd'))+
theme(legend.position = "none")

ggplot(backpack) + 
  geom_histogram(aes(x = ratio, fill = backpain_labelled), bins = 20, col = "white") + 
  facet_grid(sex ~ backpain_labelled, 
             labeller = labeller(backpain_labelled = pain_labels, sex = sex_labels)) + 
  labs(x = "\n body weight: backpack weight ratio") +
      scale_fill_manual(values=c('#f0ca41', '#5022bd'))+
theme(legend.position = "none")
```

Extension 1
```{r}
subset_backpacks <- backpack %>%
  filter(year >0) 

# look at the years
ggplot(subset_backpacks) +
  geom_bar(aes(x=year, fill = backpain_labelled)) + 
  facet_wrap(~backpain_labelled, labeller = "label_both") +
      scale_fill_manual(values=c('#f0ca41', '#5022bd'))+
theme(legend.position = "none")
```

Extension 2
```{r}
ggplot(subset_backpacks)+
  geom_bar(aes(x=backpack_weight)) + 
  facet_wrap(~year, ncol = 3) + 
  xlab("backpack weights")

#dev.off()
```

