```{r}
library(tidyverse)
library(CodeClanData)
library(janitor)
```
q1
```{r}
Weather_forecast_triduum <- list(
  Thursday = list(rain_chance = "high", wind_mph = 35, temperature_C = 13),
  Friday = list(rain_chance = "low", wind_mph = 25, temperature_C = 16),
  Saturday = list(rain_chance = "low", wind_mph = 19, temperature_C = 22)
)
Weather_forecast_triduum
```
q2
```{r}
Weather_forecast_triduum$Thursday$rain_chance
```

```{r}
Weather_forecast_triduum$Friday$wind_mph
```

```{r}
Weather_forecast_triduum$Thursday$temperature_C
```

q3
```{r}
weather_matrix_vector <- c(14L, 20L, 14L, 11L, 14L, 15L, 16L, 18L, 17L, 13L, 16L, 16L, 
18L, 16L)
weather_matrix <- matrix(1:7, nrow = 2, ncol = 7, byrow = TRUE)
#weather_matrix
# for (row_num in 1:dim(weather_matrix)[1]){
#   for (col_num in 1:dim(weather_matrix)[2]){
#     weather_matrix[row_num, col_num] <-  row_num * col_num
#   }
# }
weather_matrix
```

q4
```{r}
weather_matrix[2,3]
weather_matrix[2, ]
weather_matrix[, c(1, 3, 5)]
```


```{r}
#rownames(x) <- list(c)
# weather_matrix
# for (row_num in 1:dim(weather_matrix)[1]){
#   for (col_num in 1:dim(weather_matrix)[2]){
#     product_matrix[row_num, col_num] <-  row_num * col_num
#   }
# }
# product_matrix
```
q5
```{r}
# The_answer_is <- function(x) {
#   if(x < 10){
#     return(x)
#       if(x > 10) {
#       return(x / 10) &&
#         print("The answer is", x) 
#     } else {
#       print("Invalid Input")
#     }
#     }
# }

```

```{r}
The_answer_is <- function(x){
  if(is.numeric(x)){
    if (x > 10){
      x <- x/10
      }
    paste("The answer is", x)
  }else{
    if(is.character(x)){
      paste("The answer is", x)
    }else{
      paste("Invalid Input")
    }
    }
  }
    

```

```{r}
answer_or_divide <- function(x) {
  if (is.character(x)) {
    return(paste("The answer is: ", x))
  }
is_small <-  x < 10
  if (is.numeric(x)) {
    if (is_small) {
      return(x)
    } else {
      return(x / 10)
    }
  }

  return("Invalid input")
}

```
is_small = x < 10
```{r} 
a <- c(1, 2, 3)
b <- c(1, 3, 2)

a == b

sort(a) == sort(b)

all(a == b)

Similarity_checker <- function(x){
  if (a == b) {
    print("Exactly the same")
    print("The same")
    print("Different")
  }
}
```

```{r}
if (!is_manual) {
  do this
}
mtcars %>% 
  select(am) %>% 
  mutate(is_manual = am == 1)
```

q6
```{r}
a <- c(1, 2, 3)
b <- c(1, 3, 2)

a == b

sort(a) == sort(b)

all(a == b)
if (all(a %in% b)){
  DO SOMETHING IF TRUE
}else{
 if(all( ADD ANOTHER COMPISON USING SORT)){
    DO SOMETHING ELSE HERE
  }else{
    DO YOUR FINAL THING HERE
  }
}
#  vector_1 <- c(1, 2, 3, 4, 8)
# vector_2 <- c(2, 4, 8, 6, 10)
# Similarity_checker <- function(x){
#   if(vector_1 ==){
#     
#   } else {
#     print("Different")
#   }
# }
```

```{r}
# Learn-r.org. n.d. R Multiplication Table - Learn R - Online R Programming Tutorial. [online] Available at: <https://www.learn-r.org/r-tutorial/multiplication-table-in-r.php> [Accessed 30 June 2022].
number <- as.integer(readline(prompt = "Please enter a number for a table"))
for( t in 1:12)

{

    print ( paste (number, '*', t, '=', number * t))

}
```

```{r}
forecast_14_days_vector <- c(14L, 20L, 14L, 11L, 14L, 15L, 16L, 18L, 17L, 13L, 16L, 16L, 
18L, 16L)

forecast_14_days <- matrix(
  forecast_14_days_vector,
  nrow = 2,
  ncol = 7, 
  byrow = TRUE
)

forecast_14_days
```



```{r}
answer_or_divide <- function(x) {
  if (is.character(x)) {
    return(paste("The answer is: ", x))
  }

  if (is.numeric(x)) {
    if (x < 10) {
      return(x)
    } else {
      return(x / 10)
    }
  }

  return("Invalid input")
}
```

```{r}

is_same_vector <- function(vector_1, vector_2) {
  is_identical <- all(vector_1 == vector_2)
  
  if (all(vector_1 == vector_2)) {
    return("Exactly the same")
  }
is_similar <- all(sort(vector_1) == sort(vector_2))
  if (is_similar) {
    return("The same")
  }

  return("Different")
}
```

```{r}
a <- c(1, 2, 3, 4, 5)
b <- c(1, 4, 2, 3, 5)
c <- c(9, 4, 8, 1, 0)
```

```{r}
is_same_vector(a, a)
is_same_vector(a, b)
is_same_vector(a, c)
```

```{r}
# create empty matrix
mult_table <- matrix(nrow = 12, ncol = 12)

for (outer_factor in 1:12){
  for (inner_factor in 1:12){
    mult_table[outer_factor, inner_factor] = outer_factor * inner_factor
  }
}

mult_table
```

```{r}
make_histogram <- function(x){
  
  distinct <- sort(unique(x))
  
  for (i in distinct){
    
    count <- sum(x == i)
    
    cat(i)
    cat(" | ")
    cat(rep("*", count))
    cat("\n")
    
  }
  
}
```

```{r}
numbers <- sample(1:5, size = 50, replace = TRUE) 
numbers

make_histogram(numbers)
```