---
title: "R Notebook"
output: html_notebook
---


```{r}
library(tidyverse)
```

```{r}
library(CodeClanData)
drinks_content
```

```{r}
head(drinks_content, 5)

tail(drinks_content, 5)

dim(drinks_content)

names(drinks_content)
```

```{r}
drinks_content %>% 
  select(Beverage_category, Beverage, Beverage_prep,
Calories) %>% 
  filter(is.na(Calories)) %>% 
  summarise(count_of_missing_categories = n())
```

```{r}
drink_calories <- drinks_content %>%
  mutate(calorie_diff = Calories - 135)
```

```{r}
most_calories <- drink_calories %>% 
  group_by(Beverage_category) %>% 
  
```

You can break code down into smaller chunks to make them more manageable.

```{r}
average_calories <- pull(summarise(drinks_content, mean_cals = mean(Calories)))

average_calories
filter(drinks_content, (mean(Calories >= average_calories) == TRUE)
       
filter(drinks_content,
       Calories > average_calories)
```

```{r}
drink_col <- c("Beverage_category", "Beverage", "Beverage_prep", "Calories")
drink_cal_dat <-  select(drinks_content, all_of(drink_col))

average_Calorie <- mean(pull)
```

```{r}
mean_prep <- mean(pull(summarised_prep, mean_calories_pre))
mean_prep
```

```{r}
mutate(summarised_prep, calories_above_mean = mean_calories_pre > mean_prep)
```

```{r}
iris %>% 
  group_by(Species) %>% 
  summarize(ave_sepal_length = mean(Sepal.Length))

mean(pull(iris, sepal_Length))
```

```{r}
iris %>% 
  group_by(Species) %>% 
  summarize(ave_sepal_length = mean(Sepal.Length), Petal.Length = Petal.Length) %>% 
  summarize(mean_thing = mean(ave_sepal_length))
```

The more variables you create, the slower your machine will run.
We used to overwrite our intermediates, but we might want to take a look at old variables.
You just have to highlight the parts you're interested in to see if it's functional.
Pipes work great as a line breaker.
Space it out in a way that you understand.
Make your code make sense for you.
```{r}
drinks_content %>% select(Beverage_category,
                          Beverage, Beverage_prep, Calories) %>% 
  filter(is.na(Calories)) %>% 
  summarise(count_of_missing_calories = n())
```

```{r}
x <- c(1:4)
mutate(x, y = x + 1)
```

